### 2021-10-25 proposal-documents/white-paper/white-paper-general-preproposal.tex
acronym fix
doe templates updated with current preamble
update to white paper general

\usepackage{tabto} %general tabbed spacing
\usepackage{longtable} %need to put label at top under caption then \\ - use spacing
\usepackage[stable,hang,flushmargin]{footmisc} %footnotes in section titles and no indent; standard.bst
%\usepackage[round,semicolon]{natbib} %use 'numbers' for numbered citations; 'round' for () instead [] for inline citations
\usepackage[numbers,sort&compress]{natbib} %use 'numbers' for numbered citations; 'round' for () instead [] for inline citations; nsf.bst
\usepackage{enumitem}
\usepackage{boldline}
\usepackage{makecell}
\usepackage{booktabs}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{physics}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{lscape}
\usepackage{array}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[labelfont=bf]{caption}
\usepackage{chngcntr}
%\usepackage{hyperref}
\usepackage{sectsty}
\usepackage{textcomp}
\usepackage{lastpage}
\usepackage{xargs} %for \newcommandx
\usepackage[colorinlistoftodos,prependcaption,textsize=small]{todonotes} %makes colored boxes for commenting
\usepackage[toc,page]{appendix}
\usepackage[figure,table]{totalcount}
\usepackage[acronym,nomain,nonumberlist]{glossaries}
\makenoidxglossaries

@@

\newcommand{\edit}[1]{\textcolor{blue}{#1}} %shortcut for changing font color on revised text
\newcommand{\fn}[1]{\footnote{#1}} %shortcut for footnote tag
\newcommand*\sq{\mathbin{\vcenter{\hbox{\rule{.3ex}{.3ex}}}}} %makes a small square as a separator $\sq$
\newcommand{\sk}[1]{\sout{#1}} %shortcut for strikethrough
\newcommand{\x}{\cellcolor{lightgray}} %use to shade in table cell
\newcommand{\acf}{\acrfull} %full acronym
\newcommand{\acl}{\acrlong} %long acronym
\newcommand{\acs}{\acrshort} %short acronym

@@

%linenumbering
%\linenumbers %toggle line numbers
%\pagewiselinenumbers %reset line numbers on new page
%\modulolinenumbers[3] %line numbering interval

@@

@@

\paragraph*{Summary of the Proposed Project.}

\paragraph*{Motivation.}

@@

@@

%for a 3 page preproposal, limit above subject matter to the first page

@@

>>>>

\usepackage{tabto} %general tabbed spacing
\usepackage{longtable} %need to put label at top under caption then \\ - use spacing
\usepackage[stable,hang,flushmargin]{footmisc} %footnotes in section titles and no indent; standard.bst
%\usepackage[round,semicolon]{natbib} %use 'numbers' for numbered citations; 'round' for () instead [] for inline citations
\usepackage[numbers,sort&compress]{natbib} %use 'numbers' for numbered citations; 'round' for () instead [] for inline citations; nsf.bst
\usepackage[inline]{enumitem}
\usepackage{boldline}
\usepackage{makecell}
\usepackage{booktabs}
\usepackage{amssymb}
\usepackage{gensymb}
\usepackage{amsmath}
\usepackage{physics}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{lscape}
\usepackage{array}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[labelfont=bf]{caption}
\usepackage{chngcntr}
%\usepackage{hyperref}
\usepackage{sectsty}
\usepackage{textcomp}
\usepackage{lastpage}
\usepackage{xargs} %for \newcommandx
\usepackage[colorinlistoftodos,prependcaption,textsize=small]{todonotes} %makes colored boxes for commenting
\usepackage[toc,page]{appendix}
\usepackage[figure,table]{totalcount}
\usepackage[acronym,nomain,nonumberlist]{glossaries}
\makenoidxglossaries

\usepackage[firstpage]{draftwatermark}
\SetWatermarkText{\shortstack{DRAFT\\do not distribute}}
\SetWatermarkScale{0.35}

@@

\newcommand{\edit}[1]{\textcolor{blue}{#1}} %shortcut for changing font color on revised text
\newcommand{\fn}[1]{\footnote{#1}} %shortcut for footnote tag
\newcommand*\sq{\mathbin{\vcenter{\hbox{\rule{.3ex}{.3ex}}}}} %makes a small square as a separator $\sq$
\newcommand{\sk}[1]{\sout{#1}} %shortcut for strikethrough
\newcommand{\x}{\cellcolor{lightgray}} %use to shade in table cell

\newcommand{\acf}{\acrfull} %full acronym
\newcommand{\acl}{\acrlong} %long acronym
\newcommand{\acs}{\acrshort} %short acronym

\newcommand{\acfp}{\acrfullpl} %full acronym plural
\newcommand{\aclp}{\acrlongpl} %long acronym plural
\newcommand{\acsp}{\acrshortpl} %short acronym plural

@@

%linenumbering
\linenumbers %toggle line numbers
\pagewiselinenumbers %reset line numbers on new page
\modulolinenumbers[1] %line numbering interval

@@

{\centering 
    \textbf{Agency - Call \\
    Federal POC - , Technical POC - \\
    General budget\\
    }
\par
}

\noindent Text of call.

\newpage

@@

\paragraph*{Summary of the Proposed Project.} 
\subparagraph*{Proposal.}

\subparagraph*(Key features of the project.)

\paragraph*{Motivation.}
\subparagraph*(Context.)

@@

\subsection*{Research Focus and Workscopes.} 
\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item\textit{Workscope title (Lead - )}
        \begin{itemize}[leftmargin=*,topsep=-1ex,itemsep=-1ex,partopsep=1ex,parsep=1ex]
            \item Task 
            \item Task 
            \item Task 
            \item Task 
        \end{itemize}
    \item\textit{Concluding work (Full team)}
        \begin{itemize}[leftmargin=*,topsep=-1ex,itemsep=-1ex,partopsep=1ex,parsep=1ex]
            \item Discuss crosscutting issues
        \end{itemize}
\end{enumerate}

@@

\subparagraph*{Recently funded work.}
%for a 3 page preproposal, limit above subject matter to the first page
%research focus will have to go

\paragraph*{Unique project features.}

@@

\newpage

\begin{longtable}{|l|l|l|} %comment out for page limits
    \caption*{\textbf{Milestones.}}
    \label{tab-milestones}\\
    \hline
        \multicolumn{1}{|c|}{\textbf{Milestone}}
        &\multicolumn{1}{|c|}{\textbf{Deliverable}}
        &\multicolumn{1}{|c|}{\textbf{Completion}}\\
        \hline
        \begin{tabular}[c]{@{}l@{}}
            0. Project logistics
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
            0.1. Kick-off report, roles, and responsibilities.\\
            0.2. Annual reports.\\
            0.3. Agency administrative requirements.\\
            0.4. Final project report.\\
            0.5. Journal paper submission.\\
            0.6. Conference presentations.
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
            0.1. Y1-Q2\\
            0.2. Annually\\
            0.3. Quarterly\\
            0.4. Y3-Q4\\
            0.5. Annually\\
            0.6. Annually
        \end{tabular}
        \\
        \hline
        \begin{tabular}[c]{@{}l@{}}
            1.
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
            1.1.

        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
            1.1. YX-QN
        \end{tabular}
        \\
        \hline
        \begin{tabular}[c]{@{}l@{}}
            15. Crosscutting\\issues
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
            15.1. Identify lessons learned.\\
            15.2. Develop future pathways and partnerships.
        \end{tabular}
        &
        \begin{tabular}[c]{@{}l@{}}
            15.1. YEND-Q3\\
            15.2. YEND-Q4
        \end{tabular}
        \\
        \hline
\end{longtable}
